---
title: "nonet_ensemble regression with nonet_plot"
output: html_vignette
vignette: >
  %\VignetteIndexEntry{nonet ensemble regression with nonet plot}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

### nonet provides ensemble capabilities for regression problems. 

Below example shows the step by step implementation of nonet_ensemble and nonet_plot functions in the context of regression.
We have used Bank Note authentication data set to predict the output class variable using linear regression model.
Predictions from first linear regression model and second linear regression model are being used as inputs to the nonet_ensemble in the list form.

Let's start:

#### Load the required libraries

```{r}
library(caret)
library(ggplot2)
library(nonet)
```

#### Load the banknote_authentication dataset and explore it.
```{r}
dataframe <- data.frame(banknote_authentication)
head(dataframe)
```

### First Linear Regression Model

#### Splitting the data into train and test.
```{r}
index <- createDataPartition(dataframe$class, p=0.75, list=FALSE)
trainSet <- dataframe[ index,]
testSet <- dataframe[-index,]
```

### Feature selection using rfe in caret
```{r}
control <- rfeControl(functions = rfFuncs,
  method = "repeatedcv",
  repeats = 3,
  verbose = FALSE)
```


```{r}
outcomeName <- 'entropy'
predictors <- c("variance", "skewness", "class")
```

#### Model Training
```{r}
banknote_lm_first <- train(trainSet[,predictors],trainSet[,outcomeName],method='lm')
```

#### Predictions on testSet
```{r}
predictions_lm_first <- predict.train(object=banknote_lm_first, testSet[,predictors])
```

### Second Linear Regression Model
```{r}
index <- createDataPartition(dataframe$class, p=0.75, list=FALSE)
trainSet <- dataframe[ index,]
testSet <- dataframe[-index,]
```


### Feature selection using rfe in caret
```{r}
control <- rfeControl(functions = rfFuncs,
  method = "repeatedcv",
  repeats = 3,
  verbose = FALSE)
```

```{r}
outcomeName <- 'entropy'
predictors <- c("curtosis", "skewness", "class")
```

### Model Training
```{r}
banknote_lm_second <- train(trainSet[,predictors],trainSet[,outcomeName],method='lm')
```

### Predictions on testSet
```{r}
predictions_lm_second <- predict.train(object=banknote_lm_second, testSet[,predictors])
```

#### Create the stack of predictions
```{r}
Stack_object <- list(predictions_lm_first, predictions_lm_second)
```
#### Applying naming to the Stack_object
```{r}
names(Stack_object) <- c("lm_first", "lm_second")
```
#### nonet_ensemble
Now we need to apply the nonet_ensemble method by supplying list object and best model name as input.
Note that We have not provided training or test outcome labels to compute the weights in the weighted average ensemble method, which is being used inside the none_ensemble. Thus it uses best models prediction to compute the weights in the weighted average ensemble.
```{r}
prediction_nonet <- nonet_ensemble(Stack_object, "lm_first")
```
#### Creating the dataframe of nonet predictions and actual testSet labels to compute the accuracy
```{r}
Actual_Pred <- data.frame(cbind(actuals = testSet[,outcomeName], predictions = prediction_nonet))  
head(Actual_Pred)
```

#### Evaluation Matrix
```{r}
accuracy <- cor(Actual_Pred)
accuracy
```
#### Result Plotting: nonet_plot

Results can be plotted using the nonet_plot function.
nonet_plot is being designed to provided different plot_type options to the user so that one can plot different visualization based on their needs.

##### nonet_plot in histogram for the Actual labels in the testSet 
```{r, warning = FALSE}
plot_first <- nonet_plot(Actual_Pred$actuals, Actual_Pred$predictions, Actual_Pred, plot_type = "hist")
plot_first
```

##### nonet_plot in histogram for the nonet_ensemble predictions 
```{r, warning = FALSE}
plot_second <- nonet_plot(Actual_Pred$predictions, Actual_Pred$actuals, Actual_Pred, plot_type = "hist")
plot_second
```

### Conclusion
 
Above it can be seen that nonet_ensemble and nonet_plot can serve in a way that one do not need to worry about the outcome variables labels to compute the weights of weighted average ensemble solution. 
